### 2015-03-30 Kokkos_PG_LegacyCodeIntegration.tex
More updates in legacy section.

\chapter{Interoperability and Legacy Codes}

@@

\section{OpenMP, Pthreads and CUDA interoperability}

@@

It is important to recognize that this does not lift certain restrictions. 
For example it is not valid to allocate a view inside of an OpenMP 
parallel region, the same way as it is not valid to allocate a View 
inside a \lstinline|parallel_for| kernel. Indeed there are things which 
are slightly more cumbersome when mixing the models. Assigning 
one view to another inside a Cuda kernel or an OpenMP parallel 
region is only possible if the destination view is unmanaged. 
During dispatch of kernels with parallel for  all Views referenced 
in the functor or lambda are automatically switched into unmanaged 
mode. This would not happen when simply entering an OpenMP 
parallel region.

\subsection{Cuda interoperabiltiy}

@@

\subsection{OpenMP}

@@

\section{Legacy data structures}

@@

\subsection{Kokkos manages memory}

\subsubsection{Raw allocations}

@@

\subsection{External memory management}

@@

\subsection{Views as the fundamental data owning structure}

@@

\subsection{std::vector}

@@

@@

\section{Keeping track of data transfers}

>>>>

\section{Interoperability and Legacy Codes}

@@

\subsection{OpenMP, Pthreads and CUDA interoperability}

@@

It is important to recognize that this does not lift certain restrictions. 
For example it is not valid to allocate a view inside of an OpenMP 
parallel region, the same way as it is not valid to allocate a View 
inside a \lstinline|parallel_for| kernel. Indeed there are things which 
are slightly more cumbersome when mixing the models. Assigning 
one view to another inside a Cuda kernel or an OpenMP parallel 
region is only possible if the destination view is unmanaged. 
During dispatch of kernels with \lstinline|parallel_for|  all Views referenced 
in the functor or lambda are automatically switched into unmanaged 
mode. This would not happen when simply entering an OpenMP 
parallel region.

\subsubsection{Cuda interoperabiltiy}

@@

\subsubsection{OpenMP}

@@

\subsection{Legacy data structures}

@@

\subsection{Raw allocations through Kokkos}

@@

\subsubsection{External memory management}

@@

\subsubsection{Views as the fundamental data owning structure}

@@

\subsubsection{std::vector}

@@

Inside of parallel sections \lstinline|Kokkos::vector| switches to view semantics. That means
in particular that assignments are shallow copies. Certain functions will also throw runtime 
errors when called inside a parallel kernel. This includes resize and push.

@@

\subsection{Keeping track of data transfers}
